---
title: "Linear Models"
author: "Mia Isaacs"
date: "2024-11-07"
output: github_document
---

load packages

```{r}
library(tidyverse)
library(p8105.datasets)

set.seed(1)
```

load and clean dataset

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(stars = review_scores_location / 2) |> 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) |> 
  filter(borough != "Staten Island") |> 
  select(price, stars, borough, neighborhood, room_type) |> 
  mutate(
    borough = fct_infreq(borough),
    room_type = fct_infreq(room_type))
```

# fit some models

```{r}
fit = lm(price ~ stars, data = nyc_airbnb)

summary(fit)

names(summary(fit))

coef(fit)

fit |> 
  broom::tidy() |> 
  select(term, estimate, p.value)

fit |> 
  broom::glance()
```

try a bit more complex 

```{r}
fit =
  lm(price ~ stars + borough, data = nyc_airbnb)

fit |> 
  broom::tidy() |> 
  select(term, estimate, p.value) |> 
  mutate(
    term = str_replace(term, "borough", "Borough:")
  ) |> 
  knitr::kable(digits = 3)
```

# some diagnostics

(backtrack to some EDA)

```{r}
nyc_airbnb |> 
  ggplot(aes(x = stars, y = price)) +
  geom_point() +
  stat_smooth(method = "lm")
```

most diagnostics use residuals

```{r}
modelr::add_residuals(nyc_airbnb, fit) |> 
  ggplot(aes(x = resid)) +
  geom_histogram()
```

```{r}
modelr::add_residuals(nyc_airbnb, fit) |> 
  ggplot(aes(x = borough,  y = resid)) +
  geom_violin() +
  ylim(-200, 500)
```

residuals against stars 

```{r}
modelr::add_residuals(nyc_airbnb, fit) |> 
  ggplot(aes(x = stars,  y = resid)) +
  geom_point()
```

residuals against fitted values

```{r}
nyc_airbnb |> 
  modelr::add_residuals(fit) |> 
  modelr::add_predictions(fit) |> 
  ggplot(aes(x = pred, y = resid)) +
  geom_point()
```

# hypothesis testing

```{r}
fit |> 
  broom::tidy()

fit_null = lm(price ~ stars + borough, data = nyc_airbnb)
fit_alt = lm(price ~ stars + borough + room_type, data = nyc_airbnb)
```

look at both (when adding more than one coefficient, use ANOVA)

```{r}
fit_null |> 
  broom::tidy()

fit_alt |> 
  broom::tidy()

anova(fit_null, fit_alt) |> 
  broom::tidy()
```

# do effects differ across boroughs

first use a lot of interactions

```{r}
nyc_airbnb |> 
  lm(price ~ stars * borough + room_type * borough, data = _) |> 
  broom::tidy()
```

could just fit separate models 

```{r}
nyc_airbnb |> 
  filter(borough == "Manhattan") |> 
  lm(price ~ stars + room_type, data = _) |> 
  broom::tidy()

nyc_airbnb |> 
  filter(borough == "Brooklyn") |> 
  lm(price ~ stars + room_type, data = _) |> 
  broom::tidy()
```

get fancy and use list cols

```{r}
nyc_airbnb |> 
  nest(data = -borough) |> 
  mutate(
    model = map(data, \(x) lm(price ~ stars + room_type, data = x)),
    results = map(model, broom::tidy)
  ) |> 
  select(borough, results) |> 
  unnest(results) |> 
  select(borough, term, estimate) |> 
  pivot_wider(
    names_from = term,
    values_from = estimate
  )
```

what about room type across manhattan neighborhoods?

```{r}
nyc_airbnb |> 
  filter(borough == "Manhattan",
         neighborhood == "Chinatown") |> 
  lm(price ~ stars + room_type, data = _) |> 
  broom::tidy() 

nyc_airbnb |> 
  filter(borough == "Manhattan",
         neighborhood == "Chelsea") |> 
  lm(price ~ stars + room_type, data = _) |> 
  broom::tidy()
```

let's do this for all neighborhoods

```{r}
manhattan_neighborhood_fit_df =
nyc_airbnb |> 
  filter(borough == "Manhattan") |> 
  nest(data = -(borough:neighborhood)) |> 
  mutate(
    model = map(data, \(x) lm(price ~ stars + room_type, data = x)),
    results = map(model, broom::tidy)
  ) |> 
  select(neighborhood, results) |> 
  unnest(results)
```

look at the effect of room type

```{r}
manhattan_neighborhood_fit_df |> 
  filter(str_detect(term, "room_type")) |> 
  ggplot(aes(x = term, y = estimate)) +
  geom_boxplot()
```

```{r}
manhattan_neighborhood_fit_df |> 
  filter(str_detect(term, "room_type")) |> 
  filter(estimate > 0)

nyc_airbnb |> 
  filter(
    neighborhood == "NoHo",
    room_type == "Shared room"
  )
```












